Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-29 paper/paper.Rmd
add intro for buffering categorie

#### Spatial buffering (blockCV)

@@

#### Spatial disc (sperrorest)

@@

Another buffering oriented resampling method is "Spatial Disc" from package \pkg{sperrorest}.
The name spins from "Leave-one-disc-out" which again originates from the generic "Leave-one-out" method.
More specifically, the 'disc' which is being left our here refers to the radial area of test sets created from this method.

@@

```{r disc, fig.cap="Visualization of 'Spatial Disc' method.", out.width="50%"}
resampling_disc = rsmp("spcv_disc", folds = 5, radius = 200L, buffer = 300L)
resampling_disc$instantiate(task)

>>>>

"Buffering" refers to the idea of removing observations between test and training set by drawing a cirular buffer around one or more observations [@rest2014, @brenning2012, @blockCV].
By introducing more distance between observations, the influence of STAC should be reduced.
Buffering mostly happens in the coordinate space due to the scattered appearance of observations in this space.
\pkg{mlr3spatiotempcv} supports two "buffering" implementations: (1) "Spatial buffering" from package \pkg{blockCV} and (2) "Leave-one-disc-out cross-validation" from \pkg{sperrorest}.

#### Spatial buffering --- \pkg{blockCV}

@@

#### Leave-one-disc-out

@@

Another buffering oriented resampling method is "Leave-one-disc-out" from package \pkg{sperrorest}.
The name originates from the generic "Leave-one-out" method.
More specifically, the 'disc' which is being left our here refers to the radial area of test sets created from this method.

@@

```{r disc, fig.cap="Visualization of 'Leave-one-disc-out' method.", out.width="50%"}
resampling_disc = rsmp("spcv_disc", folds = 5, radius = 200L, buffer = 300L)
resampling_disc$instantiate(task)
